---
title: "Assignment 3"
author: "John Bowman, Amal Kadri, and David Scolari"
date: "3/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r source_path, include=FALSE echo = FALSE}
library(here)
path <- here()

source(file.path(path, 'code', 'lib.R'))
source(file.path(path, 'code', 'dengue_trees.R'))
source(file.path(path, 'code', 'green_certification.R'))
source(file.path(path, 'code', 'california_housing.R'))
```

## Podcast

1. If I want to understand how more cops in the streets affect crime, simply getting data from a few different cities and running the regression of “Crime” on “Police” is insufficient for causal identification. This is because there are likely unobserved confounding factors about cities that are responsible for the number of police and for the amount of crime. For example, if high poverty rates causes crime and leads to high amounts of police on the streets, then running the simple regression of crime on police would identify a positive relationship between crime and police. In this example, police do not cause crime, but that would be the interpretation if you took the regression result as causal. 

2. UPenn researchers use terrorism alert levels as an instrument for the amount of police on the street in order to isolate the effect of police on crime. Terrorism alert levels are a good instrument since they are not directly linked to crime (exogenous), but they do cause cities to add police to shifts (relevant). Since terror alert level is exogenous and relevant, using it as an instrument for police numbers effectively identifies the causal effect of police presence on crime. 

Tabel 2 shows that when terror level is orange (high), inducing police presence on the street exogenously elevated, the expected number of crimes is reduced by about 7. This result is significant at the 5% level. The second column includes a control for metro ridership as a proxy for the number of people on the street. With the ridership control, expected number of crimes reduces by about 6 during high terror alerts. 

3. Controlling for metro ridership makes the researchers case that the terror alert level is uncorrelated with crime stronger. Metro ridership is a proxy for foot traffic around the city. If foot traffic decreases when there is a high terror alert level, then crime might also go down because there are less potential victims in the streets. The opposite might also be true, that is, there may be a high terror alert because of a special event (a parade, perhaps), which would also mean more foot traffic and thus more chance for crime. Regardless of the sign of the effect, researchers would want to control for it, so metro ridership is added to the model. 

4. For this table, a more granular look is given to the causal relationship between increased police presence and crime rate using district 1 as a feature. The coefficient reads that the effect of an additional police officer in district 1 is associated with a 2.26 decrease in expected number of crimes and is statistically significant in District 1 at the 95% level,  whereas other districts did not exhibit a statistically significant decrease at this level.


## Dengue Trees

For this question, we chose to use number of dengue cases (rather than the log) because it seemed to predict similarly accurately and the plots/RMSE's the model generated were far more interperateable and informative than the log equivalents. 

Across model specifications and tree types, random forest regressions was a consistent winner when it came to performance. Displayed here are RMSE's for 5 regression models: A tree model with all covariates and one with some amount of feature engineering, the same for random forest, and the best boosted tree model we could make. The RMSE for the random forest with all covariates was the best performing across many train test splits. Even with some manual engineering, and cross validated tuning, we could not get the gradient boosted tree model to outperform the the random forest more than once or twice. This is a testament to why random forests are the benchmark standard for supervised learning techniques, especially since, of all the methods we tried, the random forest was the easiest to implement.

Along with `specific_humidity` and `precipitation_amt`, we chose to include PD plots for `season` and `min_air_temp_k` variables, as they both back up the same underlying temperature relationship. These choices were partially informed by the *variable importance plot* we made from our forest model, choosing variables that seemed to have the strongest effect on dengue cases. Dengue cases seem to rapidly increase at around 18 grams water per kg air, likely because this is the humidity level that allows mosquitos to thrive. Interestingly though, dengue cases seem to decrease with precipitation
```{r dengue_trees}

```

## Green Certification
For this model, we elected to use the green_rating field as opposed to just LEED of Energystar to get a big picture look at green certifications. To begin, we reviewed all the variables to exclude for the models. Property and cluster, were omitted due to lack of interrelated relationships with one another. LEED and Energystar were omitted since they both made up the feature of interest green_rating. Rent and leasing_rate were omitted because the outcome variable was a linear combination of the two, and would thus be perfectly collinear. 

The first model we tried was a lasso regression. Each time we tried to trained the model, the coefficients selected were always interactions, which is a tell-tale sign that a tree model would be a good candidate for modeling this data. 

Next we tried a random forest with the same feature specifications, which cut the RMSE almost in half from around 1250 to around 650. We compared it to a boosted tree model, but were only able to yield a RMSE of 850, making the random forest modeling method the winner.

size and stories were responsible for the greatest improvements in the model when the values were not permuted. Since rent per square foot is dependent on the size of a building and stories, the explanatory power of these variables tracks with the outcome being measured. Both size and stories partial dependence graph illustrate this similar relationship, plateauing around 2e+06 sqft and 50 stories respectively

City_Market_Rent held the highest node purity, which is to be expected since it is an aggregation of rent per square foot in the local area. Buildings in the same area are likely to be similar and thus have similar rent and leasing rates. It's partial dependence plot is a gradual slop, which coincides with this reasoning. 

age partial dependence plot sharply rises then gradually falls, representing the loss in values which occurs as a building ages. There is another spike then plateaus when the representative building turns 100 which represents the expected value that is placed on living in a historical building. This explanatory power corroborated with age's high rank on both the %IncMSE and node purity.

```{r green_certification}

```

## California Houses

```{r california_houses}
medprice_map
yhat_map
absdiff_map
```
